---
title: "Introduction to Data Science"
output:
  learnr::tutorial:
    progressive: true
    allow_skip: true
    theme: "sandstone"
runtime: shiny_prerendered
description: >
  Learn about data frames. Learn how to filter observations and select columns in a data frame. 
---

```{r setup, include=FALSE}
library(learnr)
library(tidyverse)
library(nycflights13)
library(Lahman)
library(kableExtra)
library(reactable)
library(gradethis)
tutorial_options(
  exercise.timelimit = 60,
  # A simple checker function that just returns the message in the check chunk
  exercise.checker = function(check_code, ...) {
    list(
      message = eval(parse(text = check_code)),
      correct = logical(0),
      type = "info",
      location = "append"
    )
  }
)
knitr::opts_chunk$set(error = TRUE)

music_artist_df = read.csv('music_artist.csv')
source('load_college_data.R')

```



## What is a data frame?

### Everything is stored in a data frame
A <span style="color: red;">**data frame**</span> consists of rows and columns. 

- the <span style="color: red;">**rows**</span> represent observations 
- the <span style="color: red;">**columns**</span> represent the information collected on each observation. 

Click *Run Code* button to see an example of data frame that has some top Artist from last year's billboard chart.


```{r viewdata, exercise = TRUE, exercise.eval = FALSE}
music_artist_df
```



### Quick Question 1

```{r longsong_Q1, echo = FALSE}
question("Which artist had the longest song based on the data frame? ",
         answer("Olivia Rodrigo", correct = TRUE),
         answer("The Weekend", message = "His song was the shortest"),
         answer("Dua Lipa", message = "Not Quite"),
         allow_retry = TRUE,
         random_answer_order = TRUE
)
gradethis_setup()
```

## The length of some songs

### Long Songs
You do not like long songs, so you can <span style="color: blue;">**filter**</span> a data frame to obtain only songs that are strictly less than 4 minutes. Click *Run Code* to be able to view the songs duration that are 4 minutes or more. 

```{r filter_song1, exercise = TRUE, exercise.eval = FALSE}
filter(music_artist_df,Song_Duration >= 4)
```

### Quick Question 2

**Change the mathematical expression so that you have a data frame that has songs strictly less than 4 minutes.**



```{r filter_song1_Q2, exercise = TRUE, exercise.eval = FALSE}
filter(music_artist_df,Song_Duration >= 4)
```

```{r filter_song1_Q2-solution}
filter(music_artist_df,Song_Duration < 4)
```

```{r filter_song1_Q2-check}
grade_this_code("You did it, keep up the good work!")
```



### Quick Question 3

```{r filter_Q3, echo = FALSE}
question("What is the purpose of the filter function? ",
         answer("Filter rows based on a condition", correct = TRUE),
         answer("Filter columns based on a condition", 
                message = "What reduced: rows or columns"),
         allow_retry = TRUE,
         random_answer_order = TRUE
)
```



## The Titles and Artists

### Important Columns
Lets start off with the original music artist data frame. Lets say you want primarily focus on the *Artist* and *Title* columns, you can just <span style="color: blue;">**select**</span> those columns. The code below only selects the Artist and Length.


### Quick Question 4
**Change the code so that you have a data frame that consists of the Artist and Title.**


```{r select_column1_Q4, exercise = TRUE, exercise.eval = FALSE}
select(music_artist_df, Artist, Length)
```


```{r select_column1_Q4-solution}
select(music_artist_df, Artist, Title)
```

```{r select_column1_Q4-check}
grade_this_code("Keep going!")
```



### Quick Question 5

```{r select_Q5, echo = FALSE}
question("What is the purpose of the select function? ",
         answer("Selects columns", correct = TRUE),
         answer("Selects rows", message = "What reduced: rows or columns"),
         allow_retry = TRUE,
         random_answer_order = TRUE
)
```


## Internship Opportunity

### Description
Based on your experience programming, your guidance counselor wants you to help Amber, your friend, determine which schools she should apply to based on certain criteria.

Amber's parents gave her the option of selecting schools in either Hawaii, Oregon, Utah, Nevada, California, Colorado, or Washington. Her parent’s rationale is that the she knows their relatives in these states. 

Amber wants to live on campus so that she can get the real college experience. She would like to be in a city because she always wanted to be near a lot of people.


### Quick Question 6

```{r descrip_Q6, echo = FALSE}

question_numeric(
  "How many states are they able to apply to based on their parents request? Provide an actual number." ,
  answer(7, correct = TRUE),
  allow_retry = TRUE,
  min = 7,
  max = 7,
  step = 0.01
)


```


### Quick Question 7
```{r descrip_Q7, echo = FALSE}
question("What type of college campus does Amber want to live in?",
         answer("City", correct = TRUE),
         answer("Suburban", message = "Read the second paragraph again"),
         answer("Rural", message = "Read the second paragraph again"),
         allow_retry = TRUE
)
```


### Quick Question 8

```{r descrip_Q8, echo = FALSE}
question("Does Amber want to live on campus or off campus? ",
         answer("On Campus", correct = TRUE),
         answer("Off Campus", message = "Read the second paragraph again"),
         answer("It depends where her friends live",  message = "Read the second paragraph again"),
         answer("It does not matter",  message = "Read the second paragraph again"),
         allow_retry = TRUE
)
```

## View the Data

### Look at the Data
Click *Run Code* to view the first 6 rows of 
```{r view_college_data, exercise = TRUE, exercise.eval = FALSE}
head(city_college_df)
```

Abbreviations: 

- **OOS** is Out-Of-State
- **IS** is In-State
- **LOC** is living on campus


<!-- Might Delete because it is redundant -->
### Columns
Below represents a list of information collected on each school

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}
data.frame(`Column_Names` = str_replace_all(colnames(city_college_df),'_',' ')) %>% 
  kable() %>% 
  kable_styling()
```

## Amber's Preferences

Amber is only interested in the school name, ACT Score, and out of state tuition. Amber also did better on her ACTs compared to her SATs so she only submitted her ACTs score where her score was a 32. 

Amber earned the Dwight F. Davis Memorial Scholarship for playing tennis, therefore, she does not have to worry about out of state tuition.


### Quick Question 9

```{r amber_pref_Q9, echo = FALSE}
question("Which columns do you think Amber should concentrate on based on her 
         preferences? (Select All that apply)",
         answer("School Name", correct = TRUE),
         answer("ACT Score", correct = TRUE),
         answer("Price OOS LOC", correct = TRUE),
         answer("SAT Score",message = 'Which test did she preformed better on?'),
         answer("Price IS LOC", message = 'Does she want to be In-State or Out-Of-State?' ),
         allow_retry = TRUE,
         random_answer_order = TRUE
)
```


```{r include=FALSE}
oos_city_college_df = city_college_df %>% 
  filter(State == 'OOS')
```



<!-- 2. - Action - **Select**: School Name, ACT Composite, *Out of State* -->
### Quick Question 10: 

```{r amber_pref_Q10, echo = FALSE}
question("Which line of code represents the correct way of selecting the relevant variables?",
         answer("select(oos_city_college_df,School_Name,ACT_Score,Price_OOS_LOC)", correct = TRUE),
         answer("select(School_Name, oos_city_college_df,ACT_Score,Price_OOS_LOC)",
                message = 'The data frame must be the 1st input'),
         answer("select(oos_city_college_df,School_Name,ACT_Score)",
                message = 'Remember all the variables'),
         answer("select(oos_city_college_df,School_Name,ACT_Score,Price_OOS_LOC,SAT_Score)",
                message = 'This has too many variables. Double check which variables are important'),
         answer("select(oos_city_college_df,School_Name,Price_OOS_LOC,SAT_Score)",
                message = 'Make SUre you selected the right variables'),
         allow_retry = TRUE,
         random_answer_order = TRUE
)
```


We are saving this data frame as *amber_pref_df* to contain columns that only pertain to Amber's preferences.



<!-- Background -->
```{r include=FALSE}
amber_pref_df =  select(oos_city_college_df,
                        School_Name,
                        ACT_Score,
                        Price_OOS_LOC)
```





### Filter based on ACT Scores

Based on Amber's ACT score, create a data frame that only contains schools that has Amber's ACT score and lower. This means you must filter, so that out all the schools that would accept her based on her ACT score.





### Quick Question 11

**Erase write expression to filter schools that will accept her score or less.**
```{r amber_pref_Q11, exercise = TRUE, exercise.eval = FALSE}
act_amber_pref_df = filter(amber_pref_df, write_expression )
```

```{r amber_pref_Q11-solution}
act_amber_pref_df = filter(amber_pref_df,  ACT_Score <= 32 )
```

```{r amber_pref_Q11-check}
grade_this_code("Amazing work!")
```


<!-- Background -->
```{r include=FALSE}
act_amber_pref_df =  filter(amber_pref_df,
                            ACT_Score <= 32)
```



### Amber's Data Frame of Schools based on her ACT score

Look over her data frame. 


```{r include=FALSE}
reactable(act_amber_pref_df)
```



### Quick Question 12
```{r amber_pref_Q12, echo = FALSE}

question_numeric(
  "How many schools would accept her based on her ACTs score?",
  answer(33, correct = TRUE),
  allow_retry = TRUE,
  min = 33,
  max = 33,
  step = 0.01
)


```




### Quick Question 13
Sort through the data, which school has the lowest ACT Score?


```{r amber_pref_Q13, echo = FALSE}
question("Sort through the data, which school has the lowest ACT Score?",
         answer("Metropolitan State University of Denver", correct = TRUE),
         answer("Brigham Young University-Provo", 
                message = "Lowest ACT Score not the highest"),
         answer("Utah State University", 
                message = "Not Quite"),
         answer("Seattle Pacific University", 
                message = "Not Quite"),
         answer("Hawaii Pacific University", 
                message = "Not Quite"),
         allow_retry = TRUE,
         random_answer_order = TRUE
)
```



