---
title: "Scratch File for College Admission"
author: "Dr. Williams"
date: "2/22/2022"
output: html_document
---
```{r}

## Load Libriaries
library(tidyverse)
library(readxl)
```

```{r}
## 2) Load data
df = read_xlsx('typical_ca_colleges.xlsx',sheet = 'typical_ca_colleges')

## Task 1: Make column names easier to use based on selected 10
```


```{r}
## 1) More than 0 enrollment
city_col_df <- df %>% 
  filter(`Enrolled Total` > 0,
         Urban %in% c(11,12,13)) %>% ## Provides only city colleges
  mutate(city_size = case_when(
    Urban == 11 ~ 'Large',
    Urban == 12 ~ 'Midsize',
    Urban == 13 ~ 'Small'
  )) %>% 
  select(-ID,
         -`Price In-State Living off Campus`,
         -`Price Out-of-State Living off Campus`, 
         -GPA,
         -`Enrolled Total`,
         -`SAT Reading 75th Percentile`,
         -`ACT English 75th Percentile`,
         -`ACT Math 75th Percentile`,
         -Private,
         -Urban,
         -Major,
         -Address)
```

```{r}
## Create variables for the solutions
solutions_city_col_df = city_col_df %>% 
  mutate(acceptance_rate =round( `Admissions Total`/`Applicants Total`,3)
         
         )

## Task 1: Make column names easier to use based on selected 10
## Task 2: Create in California variable
```



Everyone Create a new variable named: acceptance rate


## Amber's Preferences

- CONTEXT: (State why she wants each variable in the context of a student)Amber is only interested in the cost of the school, Admissions, ACT composite, out of state. Amber also did better on her ACTs compared to her SATs so she only submitted her ACTs score where her composite score was a 32. Amber has a scholarship for playing tennis from Dwight F. Davis Memorial Scholarship where she does not have to worry about out of state tuition.
  - Action - **Select**: School Name, ACT Score, *Out of State*
1. How many variable are located in this table? 

  - Action - **Filter**: Based on Amber's ACT score, filter out all the schools that would accept her based on her ACT score.

2. How many schools would accept her based on her ACTs score?


  - Action - **Filter**: Since Amber wants to go out of state, filter only schools that are out of state.
3. How many schools would accept her based on her ACTs score that are out of state?
4. Sort through the data, which school has the lowest ACT Score?


Teaching principles
 - filter, & select
 - ==, <=
 




## Jake's Preferences

- CONTEXT: Wants a large school

- Action - **Select**: School Name, Admission,Applicants,*Acceptance Rate*, ACT
  Score, *Out of State*
  
  
Teaching principles:
 - mutate, filter, & select
 - ==, <=

## Olivia's Preferences
